Paper_stuff

### 2023-09-23 Paper_stuff.Rmd
made treatment response factors

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
      )

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_treat,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

@@

@@

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

>>>>

    dim(CUDOS_Score_pre)
    dim(Mothership_post)
    length(Mothership_post$BL_CUDOS)
    length(Pre_dep)
#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
           CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
           CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx),
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                               ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                           ifelse(BL_CUXOS > 20, "Sig Anx",
                           ifelse(BL_CUDOS > 20, "Sig Dep",
                           ifelse(is.na(BL_CUXOS),NA,
                           ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                        )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                               ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                              ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                               ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                              ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                               ifelse(is.na(CUXOS_post),NA, "Subclinical"
                              ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                               ifelse(is.na(CUDOS_post),NA, "Subclinical"
                              ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                               ifelse(is.na(BL_CUXOS),NA,
                               ifelse(is.na(BL_CUDOS),NA, "Sub"
                               )))),
        Any_Sig_Post = as.factor(ifelse(CUXOS_post > 20 | CUDOS_post > 20, "Sig",
                               ifelse(is.na(CUXOS_post),NA,
                               ifelse(is.na(CUDOS_post),NA, "Sub"
                               )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                 ifelse(BL_CUXOS > 20, "Sig Anx",
                 ifelse(BL_CUDOS > 20, "Sig Dep",
                 ifelse(is.na(BL_CUDOS), NA,
                 ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                        )))))),
        Sig_Post = as.factor(ifelse(CUXOS_post > 20 & CUDOS_post > 20, "Sig Both",
                 ifelse(CUXOS_post > 20, "Sig Anx",
                 ifelse(CUDOS_post > 20, "Sig Dep",
                 ifelse(is.na(CUDOS_post), NA,
                 ifelse(is.na(CUXOS_post), NA, "Subclinical"
                        )))))),
        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Both", "Non-responder",
                            ifelse(Sig_BL == "Sig Anx" & Sig_Post == "Sig Anx", "Non-responder",
                            ifelse(Sig_BL == "Sig Dep" & Sig_Post == "Sig Dep", "Non-responder",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Anx", "Dep gone Anx not",
                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", NA
                            ))))))))

  # checking for pre scores
   (grepl("Sig Both",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre))
    &
  # Checking psot scores
  (grepl("Sig Both",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post))

        ))
              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
                                 ifelse(BL_CUDOS > 45, "Severe",
                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
                                )))))),
        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
                                 ifelse(BL_CUXOS > 45, "Severe",
                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
                                )))))),
        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
                                 ifelse(CUDOS_post > 45, "Severe",
                                 ifelse(is.na(CUDOS_post), NA, "Remission"
                                )))))),
        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
                                 ifelse(CUXOS_post > 45, "Severe",
                                 ifelse(is.na(CUXOS_post), NA, "Remission"
                                )))))))

      )
#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_treat,
                                  Mothership_post$BL_CUDOS,
                                  Mothership_post$BL_CUXOS,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post,
                                  #Extra stuff?
                                  Mothership_post$BL_Missing,
                                  Sig_BL_Anx,
                                  Sig_unresponse

                                  )) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

@@

ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=Test))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank()) +
  facet_wrap(~Sig_)

@@

```{r}
Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have dataa
  filter(!is.na(Days_complete_1)) |>
    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    Anx_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50 | CUXOS_post < 20, "Anx Responder",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & CUXOS_post < 20,  "Unresponders", "Low BL Anx"      
      )))),
    Dep_Responder = as.factor(
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
      )))),
    Treatment_Responder = as.factor(
      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      )))))))))))

 CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
 CUXOS_post
